{\fontfamily{ptm}\selectfont A Parameter Free Accelerated Proximal Gradient Method Without Restarting }

### 2025-02-13 Notebook LaTEX/R-WAPG/paper3.tex
>w<, fixing cringe shit

\usepackage{ifthen}\newboolean{draftmode}\setboolean{draftmode}{false}
\input{presets/wang/input.tex}
\input{presets/misc.tex}
\input{presets/julia_lstlisting.tex}

@@

\begin{abstract} 
    \noindent
    We study the accelerated proximal gradient method where the sequence that controls the momentum term doesn't follow the Nesterov's rule. 
    The paper proposed R-WAPG, a generic algorithm that unifies the convergence results for strongly convex and convex where the extrapolation constant is characterized by a sequence that is much weaker than the Nesterov's rule. 
    The R-WAPG provides a unified framework for several notable Euclidean variants of FISTA and verify their convergence. 
    In addition, we also proposed the convergence rate of strongly convex objective with a constant momentum term. 
    We reformulate R-WAPG so that it doesn't require any parameter without using the idea of restarting which we call ``Free R-WAPG". 
    Explorative numerical experiments were conducted to show its competitive convergence. 
\end{abstract}

\noindent{\bfseries 2010 Mathematics Subject Classification:}
Primary 90C30, 90C25, 65K10; Secondary 65Y20. 
\noindent{\bfseries Keywords: } Convex optimization, Nesterov's acceleration, Proximal gradient, Convergence rate.

@@

        Finally, we did the tedious work and present three equivalent forms of R-WAPG in Section \ref{sec:rwapg-equiv-repr} that are comparable to notable Euclidean variants of FISTA and beyond. This shows the descriptive power of our R-WAPG framework. 

@@

        Finally, in Section \ref{sec:free-rwapg} gives a formulation of a parameter free version of R-WAPG algorithm and showcase the numerical experiments for regression, LASSO.

@@

    Using $\overline \RR$ we model a general convex function $g: Q \rightarrow \RR$ as a function on $\RR$. 
    If $x \in \RR^n \setminus Q$ then $g(x) = \infty$ by definition. 

@@

\section{Stepwise formulation of weak accelerated proximal gradient}\label{sec:stepwise-stuff}
    The goal of this section is to build the R-WAPG algorithm which is described in the Definition \ref{def:wapg} of the next section. 
    \par 
    Definition \ref{def:stepwise-wapg} which describes what happens at a single iteration of the R-WAPG algorithm. 
    It defines a procedure of generating $x_{k + 1}, v_{k + 1}$ given any $x_k, v_k$. 
    Proposition \ref{prop:stepwise-lyapunov} states the inequality that describes a decreasing quantity that involves $F(x_k), F(x_{k + 1})$ at each single iteration. 
    \begin{assumption}
        Given $x_k, y_k, v_k$ where $k \in \mathbb Z_+$, we define the following quantities
        \begin{align}
            g_k &\defeq L(y_k - T_L y_k), 
            \label{eqn:grad-map}
            \\
            l_F(x; y_k) &\defeq F(T_Ly_k) + \langle g_k, x - y_k\rangle + \frac{1}{2L}\Vert g_k\Vert^2, 
            \label{eqn:lower-linearization}
            \\
            \epsilon_{k} &\defeq F(x_k) - l_F(x_k; y_k), 
            \label{eqn:regret}
        \end{align}
        Observe that by convexity of $F$, $\epsilon_k \ge 0$ for all $x_k, L > 0$. 
        To see, use Theorem \ref{thm:prox-grad-ineq} and let $y = y_k, x = x_k$ which gives: 
        \begin{align*}
            F(x_k) - F(T_Ly_k)
            - \langle L(y_k - T_Ly_k),x_k - y_k \rangle
            - \frac{L}{2}\Vert y_k - T_Ly_k\Vert^2
            - \frac{\mu}{2}\Vert x_k - y_k\Vert^2
            &\ge 0
            \\
            \iff 
            F(x_k) - F(T_Ly_k)
            - \langle g_k,x_k - y_k \rangle
            - \frac{1}{2L}\Vert g_k\Vert^2
            &\ge 0. 
        \end{align*}
    \end{assumption}

@@

@@

@@

                    + \langle v_k - x^*, \mu\alpha_k(y_k - v_k)\rangle,     

@@

        Simply adding both side of Equations \eqref{eqn:stepwise-lya-proof-step-1}, \eqref{eqn:stepwise-lya-proof-step-2}, it follows: 

@@

@@

    This section reduces Definition \ref{def:wapg} into simpler forms that are comparable to what commonly appears in the literatures. 

>>>>

\usepackage{ifthen}\newboolean{draftmode}\setboolean{draftmode}{true}
\input{presets/wang/input.tex}
\input{presets/misc.tex}
\input{presets/julia_lstlisting.tex}

@@

\begin{abstract} 
    \noindent
    We study the accelerated proximal gradient method where the sequence that controls the momentum term doesn't follow the Nesterov's rule. 
    The paper proposed R-WAPG, a generic algorithm that unifies the convergence results for strongly convex and convex where the extrapolation constant is characterized by a sequence that is much weaker than the Nesterov's rule. 
    The R-WAPG provides a unified framework for several notable Euclidean variants of FISTA and verify their convergence. 
    In addition, we also study the convergence rate of strongly convex objective with a constant momentum term. 
    We reformulate R-WAPG so that it doesn't require any parameter without using the idea of restarting which we call ``Free R-WAPG". 
    Explorative numerical experiments were conducted to show its competitive convergence. 
\end{abstract}

\noindent{\bfseries 2010 Mathematics Subject Classification:}
Primary 90C30, 90C25, 65K10; Secondary 65Y20. 
\noindent{\bfseries Keywords: } 
\\
Convex optimization, Nesterov's acceleration, Proximal gradient, Convergence rate.

@@

        Finally, we did the necessary work and present three equivalent forms of R-WAPG in Section \ref{sec:rwapg-equiv-repr} that are comparable to notable Euclidean variants of FISTA and beyond. This shows the descriptive power of our R-WAPG framework. 

@@

        Finally, Section \ref{sec:free-rwapg} gives a formulation of a parameter free version of R-WAPG algorithm and showcase the numerical experiments for regression, LASSO.

@@

    Using $\overline \RR$ we model a general convex function $g: \RR^n \rightarrow \overline{\RR}$ as a function on $\RR$.  

@@

\section{Stepwise formulation of weak accelerated proximal gradient}\label{sec:stepwise-stuff}
    The goal of this section is to build the R-WAPG algorithm which is described in the Definition \ref{def:wapg} of the next section. 
    \par 
    Definition \ref{def:stepwise-wapg} describes one iteration of the R-WAPG algorithm. 
    It defines the procedure of generating $x_{k + 1}, v_{k + 1}$ given any $x_k, v_k$. 
    Proposition \ref{prop:stepwise-lyapunov} states the inequality \eqref{ineq:stepwise-lya-2}  of a decreasing quantity involving $F(x_k), F(x_{k + 1})$ at each iteration.
    \par
    The assumption below is crucial to describing the convergence rate of the R-WAPG and it requires the convexity assumption on $F$. 
    \begin{assumption}
        Given $x_k, y_k, v_k$ where $k \in \mathbb Z_+$, we define the following quantities
        \begin{align}
            g_k &\defeq L(y_k - T_L y_k), 
            \label{eqn:grad-map}
            \\
            l_F(x; y_k) &\defeq F(T_Ly_k) + \langle g_k, x - y_k\rangle + \frac{1}{2L}\Vert g_k\Vert^2, 
            \label{eqn:lower-linearization}
            \\
            \epsilon_{k} &\defeq F(x_k) - l_F(x_k; y_k), 
            \label{eqn:regret}
        \end{align}
        Observe that by convexity of $F$, $\epsilon_k \ge 0$ for all $x_k, L > 0$. 
        To see, use Theorem \ref{thm:prox-grad-ineq} and let $y = y_k, x = x_k$ which gives: 
        \begin{align*}
            F(x_k) - F(T_Ly_k)
            - \langle L(y_k - T_Ly_k),x_k - y_k \rangle
            - \frac{L}{2}\Vert y_k - T_Ly_k\Vert^2
            - \frac{\mu}{2}\Vert x_k - y_k\Vert^2
            &\ge 0
            \\
            \iff 
            F(x_k) - F(T_Ly_k)
            - \langle g_k,x_k - y_k \rangle
            - \frac{1}{2L}\Vert g_k\Vert^2
            &\ge 0. 
        \end{align*}
    \end{assumption}

@@

            \item Step 1: 

@@

            \item Step 2: 

@@

@@

            \item Step 3: adding both side of Equations \eqref{eqn:stepwise-lya-proof-step-1}, \eqref{eqn:stepwise-lya-proof-step-2}, it follows: 

@@

        % PROOF SUMMARIZATION ENDS ===========================================================

@@

    The goal of this section is to reduce Definition \ref{def:wapg} into simpler forms that are comparable to what commonly appears in the literatures. 
